CES analysis for Paul Brockway rebound paper

### 2015-09-24 Articles/Brockway_Rebound_2015/Brockway_2015.Rnw
Now creating sF and sK graphs.

<<Historical_Data_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
# Melt data for plotting
historicalDataForGraph <- melt(data = historicalData, measure.vars = c("iY", "iK", "iL", "iU"), 
                               value.name = "value", variable.name = "variable")

@@

>>>>

<<Historical_Data_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=2.5, fig.cap="Historical data.", warning=FALSE>>=
# Melt data for plotting
historicalDataForGraph <- melt(data = historicalData, measure.vars = c("iY", "iK", "iL", "iU"), 
                               value.name = "value", variable.name = "variable")

@@

<<sF-sK-graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=2.5, fig.cap="$sF$ and $sK$ values.", warning=FALSE>>=
ggplot(data=historicalData %>%
         melt(measure.vars = c("sF", "sK"),
              value.name = "value", variable.name = "variable")) + 
  geom_line(mapping = aes(x=Year, y=value, group=variable, linetype=variable)) +
  facet_grid(. ~ Country) +
  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
  scale_y_continuous(breaks=c(0, 0.5, 1.0), limits=c(0, 1)) +
  xlab("") + 
  ylab("sF, sK") +
  xy_theme()
@
